### 2025-07-28 README.Rmd
url check

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![Build Status](https://travis-ci.org/ropensci/EML.svg?branch=master)](https://travis-ci.org/ropensci/EML)
[![Windows build status](https://ci.appveyor.com/api/projects/status/u2gw24yfkvxgny96?svg=true)](https://ci.appveyor.com/project/cboettig/eml)
[![codecov](https://codecov.io/gh/ropensci/EML/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/EML)
[![CRAN status](https://www.r-pkg.org/badges/version/EML)](https://cran.r-project.org/package=EML)
![downloads](http://cranlogs.r-pkg.org/badges/grand-total/RNeXML)
[![DOI](https://zenodo.org/badge/10894022.svg)](https://zenodo.org/badge/latestdoi/10894022)

>>>>

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![Build Status](https://app.travis-ci.com/ropensci/EML.svg?branch=master)](https://app.travis-ci.com/ropensci/EML)
[![Windows build status](https://ci.appveyor.com/api/projects/status/u2gw24yfkvxgny96?svg=true)](https://ci.appveyor.com/project/cboettig/eml)
[![codecov](https://codecov.io/gh/ropensci/EML/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ropensci/EML)
[![CRAN status](https://www.r-pkg.org/badges/version/EML)](https://cran.r-project.org/package=EML)
![downloads](http://cranlogs.r-pkg.org/badges/grand-total/RNeXML)
[![DOI](https://zenodo.org/badge/10894022.svg)](https://zenodo.org/badge/latestdoi/10894022)
